FTLR proof cases

### 2018-06-29 fully-abstract-comp/ftlr-proof-cases.tex
Referencing issue
Updated seal instruction to actually check against seal range.
Do not forget to use reasonability in the store case...

      \item \label{case:ftlr:jnz-z} (jnz zero case) $k = 0$

@@

    Follows from Lemma~\ref{lem:store-reg-works}, redistributing ownership in the obvious way.

>>>>

      \item \label{case:ftlr:move-cca-etc:jnz-z} (jnz zero case) $k = 0$

@@

    From $\npair{(\Phi_S.\reg,\Phi_T.\reg)} \in \lrrg{\trust}(W_R)$, we know that $\npair{(w,w')} \in \lrvg{\trust}(W_{R,2})$, $\npair{(w_2,w_2')} \in \lrvg{\trust}(\purePart{W_{R,2}]})$ and $\npair{(\Phi_S.\reg\update{r_2}{w_2},\Phi_T.\reg\update{r_2}{w_2'})} \in \lrrg{\trust}(W_R')$ with $W_R =W_R' \oplus W_{R,2}$ (using Lemma~\ref{lem:purePart-oplus} and~\ref{lem:purePart-duplicable}).

    From reasonability of $\Phi_S$, we know that $\Phi.\reg(r_2)$ is reasonable in memory $\Phi.\mem$ up to $n-1$ steps.
    Lemma~\ref{lem:trusted-and-reasonable-is-untrusted} then tells us that $\npair{(w,w')} \in \lrv(W_{R,2})$.

    The result then follows from Lemma~\ref{lem:store-reg-works}, redistributing ownership in the obvious way.
